A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-14 1_intro.tex
Tim: spell check
show jins result in intro

FDM printers expell molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
Because the positioning system generally has an order of magnitude better resolution than the width of the nozzle,
the toolpaths for filling the arbitrary polygonal shape of a layer with extrusion beads are following the contour of that layer.

@@

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_pretty.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_pretty.png}
\caption{
Toolpaths for a wedge shape using the naive offsetting approach (top) and our approach (bottom).
Red signifies overfill and blue underfill.
}
\label{intro_wedge}
\end{figure}

>>>>

FDM printers expel molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
Because the positioning system generally has an order of magnitude better resolution than the width of the nozzle,
the toolpaths for filling the arbitrary polygonal shape of a layer with extrusion beads are following the contour of that layer.

@@

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_pretty.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_pretty.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_pretty.png}
\caption{
Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017}(middle) and our approach (bottom).
Red signifies overfill and blue underfill.
}
\label{intro_wedge}
\end{figure}
